A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-08-18 for_submission/rvaught_2018.tex
updated figure 11

\begin{abstract}
We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission. The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing sensitive upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the ouflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
\end{abstract}

@@

Figure \ref{fig:SFR_lim} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs SFR and $\log(M_*/M_{\odot})$. These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging. Taken at face value, Figure \ref{fig:SFR_lim} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR. Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission. The trend in Figure \ref{fig:detection_lim} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$. The trends in SFR and mass can be combined to show each galaxies SB vs the specific SFR, shown in the right panel of \ref{fig:sSFR_lim}. The figure shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR. If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFR, exhibit the brightest emission this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.58]{all_limits.pdf}
\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389. The left panel compares the SB with each galaxies SFR. The middle panel compares the SB with each galaxies total stellar mass. The right panel compares the SB with sSFR.  Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$. The color scheme is the same as Figure \ref{fig:ew_comb}}
\label{fig:SFR_lim}
\end{figure*}

>>>>

\begin{abstract}
We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission. The sample galaxies span SFRs in the range $4\msunperyr< SFR < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations probe unmatched surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing sensitive upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the outflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
\end{abstract}

@@

Figure \ref{fig:all_limits} shows each galaxy's 5$\sigma$ SB detection limit and the SB calculated for the galaxy TKRS 4389 vs SFR in the left panel and $\log(M_*/M_{\odot})$ in the middle panel. These figures suggest that we should be able to detect scattered \ion{Mg}{2} emission with strengths similar to that detected in TKRS 4389 in our narrowband imaging. Taken at face value, the left panel of Figure \ref{fig:all_limits} could be consistent with a positive correlation between \ion{Mg}{2} SB and SFR. Future observations are needed to verify this trend, and the possibility that objects with yet higher SFRs ($>\sim$50 $\msunperyr$) exhibit brighter \ion{Mg}{2} emission. The trend in The middle panel of Figure \ref{fig:all_limits} suggests that extended \ion{Mg}{2} emission may be brighter in lower mass galaxies. Both \cite{Erb2012} and \cite{Feltre2018} observed a similar trend in their examination of the total \ion{Mg}{2} emission strength vs. galaxy $M_*$. The trends in SFR and mass can be combined to show each galaxies SB vs the specific SFR, shown in the right panel of \ref{fig:all_limits}. The figure shows that the galaxy with detected \ion{Mg}{2} also has the highest specific SFR. If it is ultimately confirmed that low-$M_*$ galaxies with the highest SFRs, or highest specific SFR, exhibit the brightest emission this could point to a physical link between the escape velocity of galaxies and the spatial extent of wind material.

@@

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.57]{all_limitsv2.pdf}
\caption{Comparison of our detection limits to the measured extended emission of TKRS 4389. The left panel compares the SB with each galaxies SFR. The middle panel compares the SB with each galaxies total stellar mass. The right panel compares the SB with sSFR.  Our imaging is sufficiently sensitive to detect extended emission at similar strengths to the extended emission measured for TKRS 4389 with SFR $\sim 50 \msunperyr$. The color scheme is the same as Figure \ref{fig:ew_comb}}
\label{fig:all_limits}
\end{figure*}
